Automatic Cause of Death Assignment from Verbal Autopsy Narratives with ChatGPT: A Case Study of Physician Agreed Deaths in Sierra Leone from 2019-2022

### 2023-12-11 manuscript/manuscript.tex
Update manuscript

\author[1]{\fnm{Rajeev} \sur{Kamadod}}\email{rajeevk@kentropy.com}
%\equalcont{These authors contributed equally to this work.}

\author[1]{\fnm{Cheryl} \sur{Chin}}\email{cheryl.chin@unityhealth.to}
%\equalcont{These authors contributed equally to this work.}

@@

\affil*[1]{\orgdiv{Centre for Global Health Research}, \orgname{Unity Health Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{100190}, \state{Ontario}, \country{Canada}}}

\affil[2]{\orgdiv{Dalla Lana School of Public Health}, \orgname{University of Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{10587}, \state{Ontario}, \country{Canada}}}

\affil[3]{\orgdiv{Department of Surgery}, \orgname{University of Toronto}, \orgaddress{\street{Street}, \city{Toronto}, \postcode{610101}, \state{Ontario}, \country{Canada}}}

>>>>

\author[1,4]{\fnm{Rajeev} \sur{Kamadod}}\email{rajeevk@kentropy.com}

\author[1]{\fnm{Cheryl} \sur{Chin}}\email{cheryl.chin@unityhealth.to}

%\equalcont{These authors contributed equally to this work.}

@@

\author[1,3]{\fnm{Areeba} \sur{Zubair}}\email{areeba.zubair@mail.utoronto.ca}

\author[1]{\fnm{Leslie} \sur{Newcombe}}\email{leslie.newcombe@unityhealth.to}

\author[1,2]{\fnm{Prabhat} \sur{Jha}}\email{prabhat.jha@utoronto.ca}

\affil*[1]{\orgdiv{Centre for Global Health Research, St. Michael's Hospital}, \orgname{Unity Health Toronto}, \orgaddress{\street{30 Bond St}, \city{Toronto}, \postcode{M5B 1W8}, \state{Ontario}, \country{Canada}}}

\affil[2]{\orgdiv{Dalla Lana School of Public Health}, \orgname{University of Toronto}, \orgaddress{\street{155 College Street}, \city{Toronto}, \postcode{M5T 3M7}, \state{Ontario}, \country{Canada}}}

\affil[3]{\orgdiv{Department of Surgery}, \orgname{University of Toronto}, \orgaddress{\street{149 College Street}, \city{Toronto}, \postcode{M5T 1P5}, \state{Ontario}, \country{Canada}}}

\affil[4]{\orgname{Kentropy Technologies Pvt. Ltd.}, \orgaddress{\street{2nd Main Rd}, \city{Bengaluru}, \postcode{560 034}, \state{Bangalore}, \country{India}}}
